---
title: "Decade Analysis of Chinese Dramas"
author: "Understanding the industry and uncovering trends from productions released 2012-2022"
output: 
  html_document:
    toc: true
    toc_float:
      collapsed: false
date: "Last updated: May 13, 2023"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(ggplot2)
library(RSQLite)
library(knitr)
```

```{r setup2}
cdramas_df <- read.csv("../data/cdramas.csv", header = TRUE)
cast_df <- read.csv("../data/cdrama_casts.csv", header = TRUE)
genres_df <- read.csv("../data/cdrama_genres.csv", header = TRUE)

dcon <- dbConnect(SQLite(), dbname = "cdramas.sqlite")
```

```{r functions}
format_table_links <- function(table) {
  # Input table is 3+ columns in order: text, url, etc.
  table[,1] <- paste0("[", table[,1], "](https://mydramalist.com", table[,2], "){target='_blank'}")
  return(table[, c(1,3:ncol(table))])
}
```

## Motivation

Chinese dramas consist of a wide variety of genres. Over time, the industry has changed in response to new regulations, modernized thinking, and rising stars. As I've watched dramas over the years and observed the evolution of the industry through hit shows, I've noticed some trends emerge. Through concrete data, I wish to showcase these trends and uncover interesting discoveries.

## Data Source

Information about each Chinese drama is scraped from the site [MyDramaList](https://mydramalist.com/), a database consisting of release information for Asian dramas and movies. I am interested in their list of [Chinese dramas](https://mydramalist.com/search?adv=titles&ty=68&co=2&st=3&so=top), specifically dramas released in 2012 to the end of 2022. To be considered, the drama also has to be rated by at least one user. The following fields are obtained:

* Page ID (unique, used to determine URL)
* Native title
* English title
* Year of release
* Episode count
* Genres
* Tags
* Cast members

There have been 3146 dramas released in the time period of interest. There have been 77971 assignments of people to projects, for 11913 unique personnel in the industry. The code used to scrape the data is included in the [GitHub repository.](https://github.com/kary5678/cdramas)

## Growth of the Industry

Over time, it seems that there are more and more hit shows per year - which may be attributed to a growth in the number of shows released. To determine if this is the case, the histogram below displays the number of dramas that have been released every year for the past decade.

```{r fig.height=4}
ggplot(data=cdramas_df, aes(x=factor(year)))+
  geom_bar()+
  labs(title="Number of Chinese Dramas Released 2012-2022",
       x="Year", y="Dramas Released")+
  theme_minimal()
```

Over time, there has been a general increase in the number of dramas released per year. There is a notable spike from 2019 to 2020; the jump is over 100 dramas. Perhaps the increase can be attributed to the COVID-19 quarantine periods, as there is more demand for indoor entertainment.


```{r}
ggplot(data=cdramas_df, aes(x=factor(year), y=eps))+
  geom_boxplot()+
  labs(title="Distribution of Chinese Drama Episode Counts 2012-2022",
       x="Release Year", y="Episode Count")+
  theme_minimal()
```

## Fun Facts

In this section, I will quickly satisfy some of the curiosities I've had with regards to the Chinese drama scene.

### The Longest Dramas

Many of my friends complain about the long episode count of Chinese dramas. What are the top 20 longest dramas by episode count?

```{r}
# Identify longest dramas
most_eps <- dbGetQuery(dcon, "
  SELECT title_en, title_zh, mdl_url, year, eps
  FROM cdramas
  ORDER BY eps DESC LIMIT 20")
most_eps$title_en <- paste0(most_eps$title_en, " (", most_eps$title_zh,")")
most_eps <- format_table_links(subset(most_eps, select=-title_zh))
knitr::kable(most_eps, col.names=c("Title", "Year", "Episodes"), row.names=TRUE)
```

### Misclassified Dramas

One thing I disagree with the MDL site on is the classification of wuxia dramas. Per Wikipedia, wuxia "is a genre of Chinese fiction concerning the adventures of martial artists in ancient China." Many titles are classified on MDL as wuxias when in reality they are xianxias or xuanhuans with fantasy elements. Which dramas aren't actually wuxias?

```{r}
# Identify fantasy "wuxia" dramas
wuxias <- dbGetQuery(dcon, "
  SELECT title_en, title_zh, mdl_url, year, eps
  FROM cdramas
  WHERE genres LIKE '%Fantasy%' AND genres LIKE '%Wuxia%'
  ORDER BY year DESC")
wuxias$title_en <- paste0(wuxias$title_en, " (", wuxias$title_zh,")")
wuxias <- format_table_links(subset(wuxias, select=-title_zh))
knitr::kable(wuxias, col.names=c("Title", "Year", "Episodes"), row.names=TRUE)
```

## The Love of "Love"

Something that bothers me is the use of the word "love" in most titles, when the native title has nothing to do with the word.

### Top Words Used

From the scraped data, there are 10943 words when all English titles are broken down, and 16728 characters across all native titles. Let's see what the most common words/characters are across all titles.

```{r word count}
# Find the top words used in drama titles
title_words <- gsub("[^A-Za-z0-9\\' ]", " ", paste(cdramas_df$title_en, collapse=" ")) #single string
title_words <- unlist(strsplit(tolower(title_words), "\\s+")) #character vector of all words
word_freq <- sort(table(title_words), decreasing = TRUE)[1:20]

# Find the top words used in the native titles
title_chars <- gsub("\\s+", "", paste(cdramas_df$title_zh, collapse = ""))
title_chars <- unlist(strsplit(title_chars, split = ""))
char_freq <- sort(table(title_chars), decreasing = TRUE)[1:20]

top_words <- t(data.frame(words = paste0(rownames(word_freq), " (", word_freq, ")"),
                          chars = paste0(rownames(char_freq), " (", char_freq, ")")))
rownames(top_words) <- c("English:", "Native:")
knitr::kable(top_words, align = paste0(rep("c", 20), collapse=""),
             col.names = 1:20,
             caption="Top 20 Words Used in Titles (With Counts)")
```

Excluding common particles such as "the" and "of", which occur the most often to no surprise, there are 386 occurrences of the word "love". To put this in perspective, there are 3146 dramas. Furthermore, not all 386 of these dramas actually use the word "love" in the native title. 


### Love Introduced in Translation

How many of these titles with the word "love" in the English title actually use the word love (or a similar term) in the native title?

```{r}
# Find the number of dramas with love in their English title
love_count <- dbGetQuery(dcon, "
  SELECT count(*) as love_count
  FROM cdramas
  WHERE LOWER(cdramas.title_en) LIKE '%love%'")
love_count <- love_count$love_count

# Find the number of dramas with love in both English and native title
love_titles <- dbGetQuery(dcon, "
  SELECT count(*) as love_count
  FROM cdramas
  WHERE LOWER(cdramas.title_en) LIKE '%love%' AND 
        (cdramas.title_zh LIKE '%爱%' OR cdramas.title_zh LIKE '%恋%' OR
        cdramas.title_zh LIKE '%喜欢%')")
love_titles <- love_titles$love_count

# Create data
data <- data.frame(
  group = c("Yes", "No"),
  value = c(love_titles, love_count-love_titles))

# Compute the position of labels
data <- data %>% 
  arrange(desc(group)) %>%
  mutate(prop = value / sum(data$value) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )

# Basic piechart
ggplot(data, aes(x="", y=prop, fill=group)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + 
  theme(legend.position="none") +
  labs(title='Of dramas that involve the word "love" in the English title,
       does the native title involve the word "love" too?')+
  geom_text(aes(y = ypos, label = paste(group, value, sep="\n")), color = "white", size=6) +
  scale_fill_brewer(palette="Set2")
```

### Where is Love?

Not only is the word "love" in many localized titles, there is also a pattern to its location in titles. For example, some hit dramas' titles include Ashes of Love, Eternal Love, and Intense Love. It seems that the localization is very formulaic - but is this actually the case? Or is there an even spread in the location of the word "love"?

```{r}
# How many titles end with the word love
love_end <- dbGetQuery(dcon, "
  SELECT count(*) as love_count
  FROM cdramas
  WHERE LOWER(cdramas.title_en) LIKE '%love'")
love_end <- love_end$love_count

# How many titles begin with the word love
love_start <- dbGetQuery(dcon, "
  SELECT count(*) as love_count
  FROM cdramas
  WHERE LOWER(cdramas.title_en) LIKE 'love%'")
love_start <- love_start$love_count

# Create data
data2 <- data.frame(
  group = c("Start", "Middle", "End"),
  value = c(love_start, love_count-love_start-love_end, love_end))

# Compute the position of labels
data2 <- data2 %>% 
  arrange(desc(group)) %>%
  mutate(prop = value / sum(data$value) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )

# Basic piechart
ggplot(data2, aes(x="", y=prop, fill=group)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + 
  theme(legend.position="none") +
  labs(title='Of dramas that include the word "love" in the English title, 
          where in the title does the word "love" occur?')+
  geom_text(aes(y = ypos, label = paste(group, value, sep="\n")), color = "white", size=6) +
  scale_fill_brewer(palette="Set2")
```

Most of the English titles contain the word "love" at the very end of the title, as I have observed. However, the spread in the location of the word is arguably more even than I thought it was initially.

## Examination of Industry Personnel

### Hard Working Cast Members

```{r}
# Find people who have been in the most dramas (can include directors, etc.)
hubs <- dbGetQuery(dcon, "
  SELECT actor, actor_url, count(*)
  FROM casts
  GROUP BY actor_url
  ORDER BY count(*) DESC LIMIT 20")
hubs <- format_table_links(hubs)
colnames(hubs) <- c("Person", "Dramas")
knitr::kable(hubs, caption="People Who Have Worked on the Most Dramas",
             row.names=TRUE)
```

#### Most Hard Working Since 2018

```{r}
# Find actors who have been in the most dramas since 2018
hubs2 <- dbGetQuery(dcon, "
  SELECT actor, actor_url, count(*)
  FROM cdramas INNER JOIN casts ON cdramas.mdl_url = casts.mdl_url
  WHERE year >= 2018 AND LOWER(casts.type) LIKE '%role%'
  GROUP BY actor_url
  ORDER BY count(*) DESC LIMIT 20")
hubs2 <- format_table_links(hubs2)
colnames(hubs2) <- c("Person", "Dramas")
knitr::kable(hubs2, caption="People Who Have Worked on the Most Dramas Since 2018",
             row.names=TRUE)
```

### Most Romantic People

```{r}
# Who are actors most involved in Romance dramas?
hubs_romance <- dbGetQuery(dcon, "
  SELECT actor, actor_url, count(*) as num_dramas
  FROM cdramas INNER JOIN casts ON cdramas.mdl_url = casts.mdl_url
  WHERE LOWER(cdramas.genres) LIKE '%romance%' AND 
        LOWER(casts.type) LIKE '%role%'
  GROUP BY actor_url
  ORDER BY count(*) DESC LIMIT 20")
hubs_romance <- format_table_links(hubs_romance)
colnames(hubs_romance) <- c("Person", "Dramas")
knitr::kable(hubs_romance, row.names=TRUE,
             caption="People Who Have Been Involved in the Most Romance Dramas")
```

### Most Involved Dramas

```{r}
# Find dramas with the largest cast size
hubs_dramas <- dbGetQuery(dcon, "
  SELECT cdramas.title_en, cdramas.title_zh, cdramas.mdl_url, count(*)
  FROM cdramas INNER JOIN casts ON cdramas.mdl_url = casts.mdl_url
  GROUP BY cdramas.mdl_url 
  ORDER BY count(*) DESC LIMIT 20")
hubs_dramas$title_en <- paste0(hubs_dramas$title_en, " (", hubs_dramas$title_zh,")")
hubs_dramas <- format_table_links(subset(hubs_dramas, select=-title_zh))
colnames(hubs_dramas) <- c("Drama", "Personnel")
knitr::kable(hubs_dramas, row.names=TRUE,
             caption="Dramas That Involve the Most People")
```

## Genre Breakdown

### Most Common Genres

There are 32 unique genres across the dramas analyzed, although the dramas can be multiple genres. What are the most common genres?

```{r}
genre_counts <- genres_df %>%
  select(-c(mdl_url, title_en, title_zh, genres)) %>%
  colSums %>%
  as.data.frame()
colnames(genre_counts) <- "Count"
genre_counts$Genre <- rownames(genre_counts)
genre_counts$Genre <- gsub("Sci.Fi", "Sci-Fi", genre_counts$Genre)
genre_counts$Genre <- gsub("Martial.Arts", "Martial Arts", genre_counts$Genre)
genre_counts$Genre <- factor(genre_counts$Genre, levels=
                               genre_counts$Genre[order(genre_counts$Count)])
ggplot(genre_counts, aes(x=Genre, y=Count))+
  geom_bar(stat="identity", fill="darkturquoise")+
  coord_flip(expand=FALSE)+
  labs(title="Number of Dramas of Each Genre",
       y="Number of Dramas", x="")+
  theme_minimal()
```

### Most Common Tags

```{r}
dbDisconnect(dcon)
```
