---
title: "Decade Analysis of Chinese Dramas"
author: "Understanding the industry and uncovering trends from productions released 2012-2022"
output: 
  html_document:
    toc: true
    toc_float:
      collapsed: false
date: "Last updated: May 9, 2023"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

cdramas_df <- read.csv("../data/cdramas.csv", header = TRUE)
cast_df <- read.csv("../data/cdrama_casts.csv", header = TRUE)
```

```{r libraries}
library(ggplot2)
```

## Motivation

Chinese dramas consist of a wide variety of genres. Over time, the industry has changed in response to new regulations, modernized thinking, and rising stars. As I've watched dramas over the years and observed the evolution of the industry through hit shows, I've noticed some trends emerge. Through concrete data, I wish to showcase these trends and uncover interesting discoveries.

## Data Source

Information about each Chinese drama is scraped from the site [MyDramaList](https://mydramalist.com/), a database consisting of release information for Asian dramas and movies. I am interested in their list of [Chinese dramas](https://mydramalist.com/search?adv=titles&ty=68&co=2&st=3&so=top), specifically dramas released in 2012 to the end of 2022. To be considered, the drama also has to be rated by at least one user.

## Growth of the Industry

```{r fig.height=4}
ggplot(data=cdramas_df, aes(x=factor(year)))+
  geom_bar()+
  labs(title="Number of Chinese Dramas Released 2012-2021",
       x="Year", y="Dramas Released")+
  theme_minimal()

ggplot(data=cdramas_df, aes(x=factor(year), y=eps))+
  geom_boxplot()+
  labs(title="Distribution of Chinese Drama Episode Counts 2012-2022",
       x="Release Year", y="Episode Count")+
  theme_minimal()
```

## Fun Facts

## The Love of "Love"

## Hard Working Cast Members
